Motional Ground-State Cooling Outside the Lamb-Dicke Regime

### 2017-07-09 paper.tex
Correct number

\begin{abstract}
  We report Raman sideband cooling of a single sodium atom to its three-dimensional
  motional ground state in an optical tweezer.
  Despite having a very large Lamb-Dicke parameter, high initial temperature, and
  large differential AC Stark shifts in the excited state,
  we achieved a ground-state preparation fidelity of $77(4)\%$ after a few hundred ms of cooling.
  Our technique includes addressing very high-order sidebands and
  fast modulating of optical tweezer trap.
  We demonstrate that Raman sideband cooling to the 3D motional ground state is applicable
  outside the Lamb-Dicke regime, for example in
  systems where tight confinement and low initial temperature are difficult to realize.
  This is particularly relevant for systems which are challenging to laser-cool,
  such as molecules and exotic atoms,
  and opens up the possibility to gain quantum motional control of these systems.
\end{abstract}

@@

Our final cooling results are shown in Fig.~\ref{f-radial} and \ref{f-axial}.
In total, 1000 cooling pulses (for \fxnote{??} ms) are applied along three axes with
cooling begins on the radial second order to remove most energy initially.
To characterize the single atom thermal occupation before and after cooling,
we perform Raman sideband thermometry before and after cooling\fxnote{add citation?}.
\fxnote{How is the thermometry done? pulse duration etc.}
For the more tightly confined radial directions (non-degenerate),
we observe clear first-order heating, first-order cooling,
and second-order cooling sidebands before RSC as is shown in red in Figure \ref{f-radial}A.
After cooling, the first and second order cooling sidebands on both radial axes are suppressed.
Given the absence of the second order cooling sideband, we perform sideband thermometry
by taking the ratio of the peaks of first-order cooling and heating sidebands to measure $\bar n / (\bar n + 1)$ \fxnote{cite}.
We found $\{\bar n =,\bar n =\}$, which corresponds to a ground state population of $90(2)\%$
and $94(3)\%$ along the two radial directions.
It is important to note that the simple sideband thermometry formula assumes the coupling strength
to be proportional to $\sqrt{n}$. Outside of the Lamb-Dickes regime,
the coupling strength deviates from this simple scaling rule rapidly
as shown in figure \ref{f-ld}A. Since the Raman spectroscopy is performed
with a relatively large Raman Lamb-Dickes parameters $\eta^R$,
we therefore use an independent measurement of Rabi flopping on the carrier (Fig. \ref{f-radial}B)
and first-order heating(Fig. \ref{f-radial}C) sidebands
to verify the ground-state population~\cite{Meekhof1996}.
The data is fitted using the same Monte-Carlo simulation we used to simulate the cooling
which yields $89(2)\%$ and $92(2)\%$ and show good agreement with
the population extracted from the sideband thermometry.
We also extracted the initial temperature before cooling
from the motional-state decohered Rabi flopping and obtained \fxnote{70(?)} $\mu$K.

>>>>

\begin{abstract}
  We report Raman sideband cooling of a single sodium atom to its three-dimensional
  motional ground state in an optical tweezer.
  Despite having a very large Lamb-Dicke parameter, high initial temperature, and
  large differential AC Stark shifts in the excited state,
  we achieved a ground-state preparation fidelity of $77(4)\%$ after $100$ ms of cooling.
  Our technique includes addressing very high-order sidebands and
  fast modulating of optical tweezer trap.
  We demonstrate that Raman sideband cooling to the 3D motional ground state is applicable
  outside the Lamb-Dicke regime, for example in
  systems where tight confinement and low initial temperature are difficult to realize.
  This is particularly relevant for systems which are challenging to laser-cool,
  such as molecules and exotic atoms,
  and opens up the possibility to gain quantum motional control of these systems.
\end{abstract}

@@

Our final cooling results are shown in Fig.~\ref{f-radial} and \ref{f-axial}.
In total, $1000$ cooling pulses (for $100$ ms) are applied along three axes with
cooling begins on the radial second order to remove most energy initially.
To characterize the single atom thermal occupation before and after cooling,
we perform Raman sideband thermometry before and after cooling\fxnote{add citation?}.
\fxnote{How is the thermometry done? pulse duration etc.}
For the more tightly confined radial directions (non-degenerate),
we observe clear first-order heating, first-order cooling,
and second-order cooling sidebands before RSC as is shown in red in Figure \ref{f-radial}A.
After cooling, the first and second order cooling sidebands on both radial axes are suppressed.
Given the absence of the second order cooling sideband, we perform sideband thermometry
by taking the ratio of the peaks of first-order cooling and heating sidebands to measure $\bar n / (\bar n + 1)$ \fxnote{cite}.
We found $\{\bar n =,\bar n =\}$, which corresponds to a ground state population of $90(2)\%$
and $94(3)\%$ along the two radial directions.
It is important to note that the simple sideband thermometry formula assumes the coupling strength
to be proportional to $\sqrt{n}$. Outside of the Lamb-Dickes regime,
the coupling strength deviates from this simple scaling rule rapidly
as shown in figure \ref{f-ld}A. Since the Raman spectroscopy is performed
with a relatively large Raman Lamb-Dickes parameters $\eta^R$,
we therefore use an independent measurement of Rabi flopping on the carrier (Fig. \ref{f-radial}B)
and first-order heating(Fig. \ref{f-radial}C) sidebands
to verify the ground-state population~\cite{Meekhof1996}.
The data is fitted using the same Monte-Carlo simulation we used to simulate the cooling
which yields $89(2)\%$ and $92(2)\%$ and show good agreement with
the population extracted from the sideband thermometry.
We also extracted the initial temperature before cooling
from the motional-state decohered Rabi flopping and obtained \fxnote{70(?)} $\mu$K.
